My thesis

### 2020-02-04 manuscript/index/05-appendix.Rmd
update gitignore

# List of Definitions
Model.

>>>>

# Parameter Configurations
```{r}
# load model parameters 
source("R/asr-parameters.R")
```

```{r}
# configurations table 
tab <- lapply(words, FUN = function(x) paste(x, collapse = ", "))
tab <- do.call(rbind, tab)
colnames(tab) <- c("Configurations")

```

```{r}
# combinations table
combins <- expand.grid(params) %>%
  arrange(model, feature_extraction)

# rows to drop
droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
combins <- combins[!droprows, ]
```

ASReview takes the following parameters/arguments:

- number of training data (included/excluded)
- a model
- a query strategy
- a balance strategy (fixed)
- feature extraction

```{r}
kable(tab, "latex", booktabs = TRUE) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(2, width = "30em") 
```

This leads to  `r nrow(combins)` combinations of configurations.

- Naive bayes only goes with tfidf feature extraction.
- For the feature extraction strategies we will focus on doc2vec and tfidf. (but will compute all 4)
- This leads to 3 * 7  * 4 * 3 + 1 * 7 * 1 * 3 =  273 combinations.

```{r}
names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy", "Training data [included/excluded]")
combins %>%
  kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
  kable_styling(latex_options = c("repeat_header")) 
```

# List of Definitions

Balance Strategy

Model.

### 2020-02-04 manuscript/index/index.Rmd
update gitignore

---
author: 'Gerbrich Ferdinands'
date: 'May 2020'
institution: 'Utrecht University'
division: 'Faculty of Social Sciences'
advisor: 'prof. dr. Rens van de Schoot'
# If you have more two advisors, un-silence line 7
altadvisor: 'Jonathan de Bruin, Raoul Schram'
department: 'Methodology and Statistics'
degree: 'Master of Science'
title: 'My thesis'
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
#  thesisdown::thesis_pdf: default # yet fails to compile 
  thesisdown::thesis_gitbook: default # creates html book in _book folder.  
  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default
# If you are creating a PDF you'll need to write your preliminary content (e.g., abstract, acknowledgements) here or
# use code similar to line 22-23 for the .RMD files. If you are NOT producing a PDF, you can delete or silence lines 21-32 in this YAML header.
abstract: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = '\n  ')`
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab is 
# needed on the line after the `|`.
#acknowledgements: |
#  I want to thank a few people.
#dedication: |
#  You can have a dedication here if you wish. 
#preface: |
#  This is an example of a thesis setup to use the reed thesis document class
#  (for LaTeX) and the R bookdown package, in general.
# Specify the location of the bibliography below
bibliography: bib/asreview.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
lot: true
lof: true
# If you prefer blank lines between paragraphs, un-silence lines  40-41 (this requires package tikz)
#header-includes:
#- \usepackage{tikz}
---

@@

```{r include_packages, include = FALSE}
# This chunk ensures that the thesisdown package is
# installed and loaded. This thesisdown package includes
# the template files for the thesis.
if(!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if(!require(thesisdown))
  devtools::install_github("ismayc/thesisdown")
library(thesisdown)
```

>>>>

---
author: 'Gerbrich Ferdinands'
date: 'May 2020'
institution: 'Utrecht University'
division: 'Faculty of Social Sciences'
advisor: 'prof. dr. Rens van de Schoot'
# If you have more two advisors, un-silence line 7
altadvisor: 'Jonathan de Bruin, Raoul Schram'
department: 'Methodology and Statistics'
degree: 'Master of Science'
title: 'My thesis'
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
  thesisdown::thesis_pdf: default # yet fails to compile 
  thesisdown::thesis_gitbook: default # creates html book in _book folder.  
#  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default
# If you are creating a PDF you'll need to write your preliminary content (e.g., abstract, acknowledgements) here or
# use code similar to line 22-23 for the .RMD files. If you are NOT producing a PDF, you can delete or silence lines 21-32 in this YAML header.
abstract: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = '\n  ')`
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab is 
# needed on the line after the `|`.
#acknowledgements: |
#  I want to thank a few people.
#dedication: |
#  You can have a dedication here if you wish. 
#preface: |
#  This is an example of a thesis setup to use the reed thesis document class
#  (for LaTeX) and the R bookdown package, in general.
# Specify the location of the bibliography below
bibliography: bib/asreview.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
lot: true
lof: true
# If you prefer blank lines between paragraphs, un-silence lines  40-41 (this requires package tikz)
#header-includes:
#- \usepackage{tikz}
---

@@

```{r include_packages, include = FALSE}
# This chunk ensures that the thesisdown package is
# installed and loaded. This thesisdown package includes
# the template files for the thesis.
if(!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if(!require(thesisdown))
  devtools::install_github("ismayc/thesisdown")
library(thesisdown)

knitr::opts_chunk$set(echo = FALSE)

source("R/packages.R")
```
